Algorithmic model for N-GREEN optical ring

### 2017-09-28 Papier NGreen/model.tex
rangement

\maketitle

\section*{Definitions, model}
We consider an optical ring composed of $k$ nodes.
We are in a discrete time model: The time is split in $N$ slot, rotating to the following position each time step $t$. The number of slots is given by the length of the ring, and the time step $t$ is the switching granularity. 
\begin{center}

We consider a ring as a graph model. The weight of the arcs is the time taken by a slot to travel the link, i.e. a multiple of $t$. The sum of all the weight of the arcs in the graph is equal to $t.N$.

\section*{Periodic process}
We define a set $\cal C$ of couple of vertices $(u,v) \in V$. Between each couple of $\cal C$, the following periodic process of period $P$ ($P$ is a multiple of $N$) is observed.
\begin{enumerate}
 \item The node $u$ receives (from another source) some latency critical data addressed to $v$.
 \item Those data are transferred to $v$ through the ring .
 \item After a computation time of the message, the node $v$ sends an answer to $u$.
\end{enumerate}
 This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.

\section*{Sending policy}
In the studied model, the nodes of the ring have a {\bf broadcast and select} policy.
When a node sends a packet on the ring, it contains data for several destinations. Every node of the ring reads all the slots and keep the data addressed to it. It copy the data of the packet in the slot, but does not remove anything. The only node that can free a slot is the one which send a packet in it.

@@

We can consider two buffers containing $x$ and $y$ amount of data, respectively for the C-RAN flow and the best effort flow.
The data in the first buffer are inserted first in the buffer of the node, and comes periodically in regard of the period $P$. 
The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.

@@

      \includegraphics[scale=0.7]{insertion.pdf}

@@

@@

\section*{Parameters}
The following parameters are considered for the study:
\begin{itemize}
 \item $k \in {3,..,10}$ nodes on the ring.
 \item The switching granularity $t = 10\mu s$. 
 \item The length of the ring = 50km. Thus $N = 25$ slots.
 \item Capacity of one slot $= 1Mb$.
 \item One slot of the ring can carry all the data stacked in $Q$ ($Q < 1Mb$).

\end{itemize}

>>>>

\maketitle
\section*{Problem}
The application we study takes place in the C-Ran context. We want to centralise calculations into a common data-center for an area of antennas distributed on the territory. The data between the RRH (antennas) and the BBU (data-center) are transiting through an optical ring. We study here only the behaviour of the ring. First, for an easier model, we consider a ring in which one or two nodes are the data-centers, and the other nodes of the ring sends some data coming from the RRH.

Every millisecond, between each couple RRH-BBU, the following periodic process is observed:
\begin{enumerate}
 \item The RRH sends some latency critical data to its BBU.
 \item Those data are transferred to the BBU through the ring .
 \item After a computation time of the message, the BBU sends an answer to its RRH.
\end{enumerate}
 This periodic process has a critical end to end latency, thus a messages has to be as little buffered as possible before being sent in the ring.
 Every messages will browse the entire ring during the process. Since the ring is approximately 50km long, a messages needs $250 \mu s$ to travel this length.
 Considering that the periodicity of the emissions ($1ms$) is greater than a ride of the ring, we take $P$ a multiple of the time needed to travel the ring.

\section*{Sending policy}
In the studied model, the nodes of the ring have a {\bf broadcast and select} policy. Then, the physical times needed to insert the data in the ring are negligible in regard of the other times.
When a node sends a packet on the ring, it contains data for several destinations. Every node of the ring reads all the slots and keep the data addressed to it. It copy the data of the packet in the slot, but does not remove anything. The only node that can free a slot is the one which send a packet in it.

@@

We can consider two buffers containing $x$ and $y$ amount of data. The first one is filled with the C-Ran data in priority, and the best effort flow if needed, the second one takes the rest of best effort flow. We consider that, even if a lot of RRH are represented by a node on the ring, the amount of C-Ran data incoming to a node is strongly lower than the capacity of a packet ($\simeq 1.2$ Gbps for each RRH, 100 Gbps into the ring).
The C-RAN data comes periodically in regard of the period $P = 1ms$. 
The best effort data comes more randomly (can be modelled by a Poisson distribution, for example), and are inserted in the buffer if $x = 0$.

@@

      \includegraphics[scale=0.7]{insertion1.pdf}

@@

\section*{Model}
We consider an optical ring composed of $k$ nodes ($k={3,...,10}$).
We are in a discrete time model: the time is split in $N$ slot, rotating to the following position each time step $t = 10 \mu s$. This value is the switching granularity.
\begin{center}

Considering a length of 50 km for the ring, we evaluate the number of slots about 25 into the ring.

@@
